\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-04-30 chapters/3_algorithm.tex
Update images and update minor details

\begin{minipage}[t]{\textwidth}
        \centering
        \begin{minipage}[t]{0.49\textwidth}
\centering
        \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
\captionof{figure}{{\small 
Example of edge contraction of $e_{uv}$. The first row represents the original graph $\mathcal{G}$ and the clustering $\Pi$ (purple lines), where green edges are not on the cut. Red bars indicate cannot-link constraints, whereas the contracted graph $\tilde{\mathcal{G}}_\Pi$ is shown in the second row. In step (ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In (iii), the two double edges $e_{ut}$ and $e_{vt}$ resulting from the contraction are replaced by a single constrained edge with updated interaction $f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}))$, where $f$ is defined in Table \ref{tab:linkage-criteria}.} 
\label{fig:edge_contraction_and_contr_graph} }
    \end{minipage}\hspace{0.01\textwidth}
    \begin{minipage}[t]{0.49\textwidth}
        \centering
\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.jpg}
\captionof{figure}{\small 
\UPDATE{Comparison of \algname{}  with (top) and without (bottom) enforcing cannot-link constraints on a toy graph with positive (green) and repulsive (red) interactions. Only contracted graph is represented; every column represent one iteration of the algorithm; the selected edge at each iteration is highlighted in yellow; constrained edges are represented with red bars. We note that the two resulting clusterings are different.}
\label{fig:algorithm_with_without_CLC}}
    \end{minipage}
\end{minipage}

@@

Given a simple graph $\mathcal{G}(V,E)$, we call the set $\Pi$ a \emph{clustering} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for every $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. In the following we denote the cluster associated with node $u$ as $S_u$.
% \begin{equation}
% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
% \end{equation}

In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ to each edge $e \in E$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms defining positively weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph. In these formalisms, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$ to each edge: the higher this weight, the greater the desire of the incident vertices to be in different clusters. 
Often, graphs $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes are also defined as $\mathcal{G}(V,E,\cost)$, where $\cost: E \rightarrow \mathbb{R}$ represents a \emph{signed interaction} that combines both attraction and repulsion into one signed scalar number: % space: make equation in line
\begin{equation}
\cost_e = w_e^+ - w_e^- \in \mathbb{R}, \quad \quad \forall e \in E
\end{equation}
Graphs that have only positive weights can be clearly seen as a special case of the previously defined graph $\mathcal{G}(V,E,w^+,w^-)$, when $w^-_e=0$ and $\cost_e \geq 0$ for every $e \in E$.

@@

@@

We now present our main contribution: a Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname) that can describe in a simple form several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.

@@

In the Supplementary material we provide a more detailed description of the algorithm and we also comment on its computational complexity (Sec. \ref{sec:complexity}).

@@

Another proposed clustering algorithm for signed graphs, named Mutex Watershed \cite{wolf2018mutex}, also introduces dynamical cannot-link constraints. In the supplementary material (Sec. \ref{sec:equivalence_MWS}) we show how it can be seen as an efficient implementation of \algname{} with the \emph{absolute-maximum} update rule defined in Table \ref{tab:linkage-criteria} and we also observe that this case the algorithm returns the same clustering with or without enforcing cannot-link constraints.

On the other hand, new variations of agglomerative clustering on signed graphs that, to our knowledge, were never mentioned in the literature are given by \algname{} with update rules \emph{mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}).

In this work we test and compare these algorithms and the five update rules listed in Table \ref{tab:linkage-criteria} that represent the most common options. 
Nevertheless, more elaborated options exist: \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}), whereas 
\cite{funke2018large} uses a \emph{quantile} update rule by populating a histogram for each inter-cluster interaction.

>>>>

@@

We consider an undirected simple graph $\mathcal{G}(V,E)$, in which nodes can represent either pixels, superpixels or voxels. We call the set $\Pi$ a \emph{clustering} with $K$ clusters if $V = \cup_{i=1}^K S_i $, $S_i \cap S_j = \emptyset$ for each $i\neq j$ and every $S \in \Pi$ induces a connected subgraph of $\mathcal{G}$. In the following we denote as $S_u$ the cluster associated with node $u$.
% \begin{equation}
% S_u \equiv S \in \Pi \,\, \text{s.t.} \,\, u \in S
% \end{equation}

In this work, we consider the problem of clustering a weighted graph $\mathcal{G}(V,E,w^+, w^-)$ with both attractive and repulsive edge attributes. The weight function $w^+: E \rightarrow \mathbb{R}^+$ associates a positive scalar attribute $w_e^+\in \mathbb{R}^+$ representing a merge affinity or a similarity measure: the higher this number, the higher the inclination of the two incident vertices to be assigned to the same cluster\footnote{Note that several formalisms for positively weighted graphs associate to each edge a positive scalar that represents a metric or distance on the graph, thus, the \emph{lower} the edge weight, the higher the attraction between the two linked nodes, contrary to our definition of $w^+: E \rightarrow \mathbb{R}^+$.}. On the other hand, $w^-: E \rightarrow \mathbb{R}^+$ associates a split tendency $w_e^- \in \mathbb{R}^+$: the higher this weight, the more the incident vertices would like to be in different clusters. 
Graphs of the type $\mathcal{G}(V,E,w^+, w^-)$ are also often defined as \emph{signed graphs} $\mathcal{G}(V,E,\cost)$, featuring signed edge weights: ${\cost_e = w_e^+ - w_e^- \in \mathbb{R}, \, \forall e \in E}$.
Graphs with purely attractive interactions are a special case of $\mathcal{G}(V,E,\cost)$ with $\cost_e \geq 0$ and $w^-_e=0$ for each $e \in E$.

@@

\begin{minipage}{\textwidth}
        \centering
        \begin{minipage}{0.49\textwidth}
\centering
        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
\captionof{figure}{ 
Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (red bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{ut}$ and $e_{vt}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}))$, see definitions in Tab.~\ref{tab:linkage-criteria}. 
\label{fig:edge_contraction_and_contr_graph} }
    \end{minipage}\hspace{0.01\textwidth}
    \begin{minipage}{0.49\textwidth}
        \centering
\includegraphics[width=0.8\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/cannot-lin-constraints.jpg}
\captionof{figure}{ 
\UPDATE{Comparison of \algname{}  with (top) and without (bottom) enforcing cannot-link constraints on a toy graph with positive (green) and repulsive (red) interactions. Only contracted graph is represented; every column represent one iteration of the algorithm; the selected edge at each iteration is highlighted in yellow; constrained edges are represented with red bars. We note that the two resulting clusterings are different.}
\label{fig:algorithm_with_without_CLC}}
    \end{minipage}
\end{minipage}

@@

We now present a Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname) that can describe in a simple form several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.

@@

In the Supplementary material we comment on the algorithm computational complexity (Sec. \ref{sec:complexity}).

@@

Mutex Watershed \cite{wolf2018mutex}, another algorithm for signed graphs, also introduces dynamical cannot-link constraints. In supplementary material (Sec. \ref{sec:equivalence_MWS}) we show how it can be seen as an efficient implementation of \algname{} with the \emph{abs-max} update rule (see Tab. \ref{tab:linkage-criteria}) and observe that in this case \algname{} returns the same clustering with or without enforcing cannot-link constraints.

On the other hand, new variations of \algname{} that, to our knowledge, were never mentioned in the literature are showed in Tab. \ref{tab:linkage-criteria} by using signed graphs and update rules \emph{mean}, \emph{max} or \emph{min}.

In this work we compare the algorithms listed in Table \ref{tab:linkage-criteria}, which represent the most common options. 
Nevertheless, more elaborated options exist: \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas 
\cite{funke2018large} uses a \emph{quantile} update rule by populating a histogram for each inter-cluster interaction.
